---
layout: post
title: "Fortune VCs"
date: 2016-5-24
output:
  html_document
share: true
categories: blog
excerpt: "What do venture capitalists look like?"
tags: [rstats]
---

```{r message=FALSE, warning=FALSE}
devtools::install_github("abresler/forbesListR")
library(forbesListR)
library(tidyr)
library(dplyr)
library(ggplot2)
```

## Fortune Lists

One of the awesome things about R is that anyone can write a package for it to grab some data. Fortune Magazine publishes all sorts of lists that were hard to grab for a long time. Then, I was browsing reddit one day and found that someone had written [a little package](https://github.com/abresler/forbesListR) to hook into the Fortune API to grab the list data and I had to give it a try. 

```{r message=FALSE, warning=FALSE}
vcs_2012_2016 <-get_years_forbes_list_data(years = 2012:2016, list_name = "Top VCs")
head(vcs_2012_2016)
```

I just want to do some quick gender and country analysis. 

```{r message=FALSE, warning=FALSE}
ggplot(vcs_2012_2016, aes(year, fill=gender)) + geom_bar()
ggplot(vcs_2012_2016, aes(year, fill=country)) + geom_bar()
```

Couple things here. First, there are a lot of NAs early on. I can't do much about that. Two results are apparent. Top VCs are almost always men. And a huge share are American men. 

```{r message=FALSE, warning=FALSE}
vc16 <- subset(vcs_2012_2016, year == 2016)
vc15 <- subset(vcs_2012_2016, year == 2015)
vc14 <- subset(vcs_2012_2016, year == 2014)
vc13 <- subset(vcs_2012_2016, year == 2013)
vc12 <- subset(vcs_2012_2016, year == 2012)
vc15 <- select(vc15, year, name, rank)
vc14 <- select(vc14, year, name, rank)
vc13 <- select(vc13, year, name, rank)
vc12 <- select(vc12, year, name, rank)
vc2012 <- head(vc12, -25)
vc13 <- head(vc13, -25)
vc14 <- head(vc14, -25)
vc15 <- head(vc15, -25)
vc16 <- head(vc16, -25)
df <- rbind(vc12, vc13, vc14, vc15)
rank <- aggregate(df$rank, list(df$name), sum)
rank$name <- rank$Group.1
rank$Group.1 <- NULL
summary(rank$x)
```

I want to visualize how rankings change over time but I can't plot every single VC that shows up on the Fortune list. So, I want to just subset those. I will only plot those whose ranking slightly below the median over the five years of the list. 

```{r message=FALSE, warning=FALSE}
merge <- merge(vcs_2012_2016, rank, by=c("name"))
merge <- subset(merge, x <= 65)
```

```{r message=FALSE, warning=FALSE}
p <- ggplot(merge, aes(factor(year), rank,
group = name, colour = name, label = name))


p1 <- p + geom_line(size=1.25) + geom_text(data = subset(merge,
                                                year == "2016"), aes(x = factor(year +
                                                                                  0.5)), size = 3.5, hjust = 0.8)
p1 + theme_bw() + theme(legend.position = "none",
                        panel.border = element_blank(), axis.ticks = element_blank()) + xlab(NULL) + ylab(NULL) + scale_y_reverse( lim=c(100,0))
```

The visual is pretty noisy, but it's a lot of names to plot and some of the changes are pretty dramatic. It's interesting to see how the top VCs have stayed that way for basically the entire history of the list. There is a lot more significant changes in rankings once you get below rank 25 or so. 